---
title: 'Faculty Search: Student Feedback'
author: 'Prepared by: Emilie Campos'
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_notebook: default
---

We appreciate the committee’s interest in gauging students’ opinions regarding the faculty search. The survey distributed to the students is an imperfect measure of a candidate’s ability to perform as an educator and researcher but we hope that this supplementary feedback will aid in your decision. We want to warn you that the sample sizes for each survery were small as a whole and wildy different for each candidate so the rankings are almost arbitrary. However, we feel that the comments section reflects student interest more appropriately.

The survey distributed to the students asked the questions, with fields for additional comments:  
1. Do you believe this person would be a good instructor?  
2. Do their research interests align with yours?  
3. Would you like to see them join the department?  


```{r, include = FALSE}
library(here) 
library(tidyverse) 
library(readxl)

gronsbell <- read_excel(here("2020-faculty-search", "data", "Faculty Search 2020_ Gronsbell (Responses).xlsx")) %>% 
  setNames(c("timestamp", "instructor", "instructor_reason", "research", "join", "add_comments")) %>% 
  select(-timestamp)

jewell <- read_excel(here("2020-faculty-search", "data", "Faculty Search 2020_ Jewell (Responses).xlsx")) %>% 
  setNames(c("timestamp", "instructor", "instructor_reason", "research", "join", "add_comments")) %>% 
  select(-timestamp)

tansey <- read_excel(here("2020-faculty-search", "data", "Faculty Search 2020_ Tansey (Responses).xlsx")) %>% 
  setNames(c("timestamp", "instructor", "instructor_reason", "research", "join", "add_comments")) %>% 
  select(-timestamp)

zhang <- read_excel(here("2020-faculty-search", "data", "Faculty Search 2020_ Zhang (Responses).xlsx")) %>% 
  setNames(c("timestamp", "instructor", "instructor_reason", "research", "join", "add_comments")) %>% 
  select(-timestamp)

meisner <- read_excel(here("2020-faculty-search", "data", "Faculty Search 2020_ Meisner, Luo, and Holbrook (Responses).xlsx")) %>% 
  select(1:4, 11, 14) %>% 
  setNames(c("timestamp", "instructor", "research", "join", "add_comments", "instructor_reason")) %>% 
  select(-timestamp)

luo <- read_excel(here("2020-faculty-search", "data", "Faculty Search 2020_ Meisner, Luo, and Holbrook (Responses).xlsx")) %>% 
  select(1, 5:7, 12, 15) %>% 
  setNames(c("timestamp", "instructor", "research", "join", "add_comments", "instructor_reason")) %>% 
  select(-timestamp)

holbrook <- read_excel(here("2020-faculty-search", "data", "Faculty Search 2020_ Meisner, Luo, and Holbrook (Responses).xlsx")) %>% 
  select(1, 8:10, 13, 16) %>% 
  setNames(c("timestamp", "instructor", "research", "join", "add_comments", "instructor_reason")) %>% 
  select(-timestamp)
```

```{r, echo = FALSE}
map_dfr(
  list(
    "Gronsbell" = gronsbell,
    "Jewell" = jewell,
    "Tansey" = tansey,
    "Zhang" = zhang,
    "Meisner" = meisner,
    "Luo" = luo,
    "Holbrook" = holbrook
  ),
  ~ data.frame(
    "instructor_mean" = mean(.x$instructor, na.rm = TRUE), 
    "join_mean" = mean(.x$join, na.rm = TRUE)
    ), 
  .id = "Candidate"
) %>% 
  arrange(desc(join_mean)) %>% 
  setNames(c("Candidate", "Good instructor", "Join Department")) %>% 
  mutate("Ranking" = seq(1, 7)) %>% 
  select(Ranking, everything())
```

Notable comments: 

- Andrew Holbrook 

  > "I think the candidate had a clear presentation, but I was a little put off by the way he answered some of the questions from the audience.  I think he would have clear lectures, but I'm unsure if I would feel comfortable coming to him if I was confused about lecture material because he didn't give me the impression that he could or would be willing to explain concepts in simpler terms to help students \"get it\"."
  
  > "His research is an area in which our department is somewhat weak, but a lot of students are interested in."
  
  > "Andrew is very knowledgeable, very friendly, and has a really strong background both in theory and computation. He's great both as a researcher and mentor, and his passion for stats is infectious."
  
  > "I've discussed statistics with Andrew several times and his explanations of difficult ideas are always very clear. He's also very patient."  
  
   > "From his job talk Andrew is good at teaching and his research is quite modern as well as with exciting applications."
   
   > "He seemed a bit abrasive and impatient."

- Wesley Tansey 
  
  > "He is a good researcher himself, and he can bring connections with high-profile labs (such as the NIH automatic cell line testing lab he mentioned during the talk)."      
  
  > "I thought his research was fascinating and his presentation of the information was good. I appreciated his emphasis on collaboration with scientific experts and the data-driven approach. As a person, he was very approachable and great to talk to! I think he can help fill the department's gap in computation and data-science methods."
  
  > "He explains things in simple and easy to understand terms, and he addressed questions from the audience really well."

- Jessica Gronsbell 

  > "Her industry experience will be helpful in mentoring students who plan to go into industry."
  
  > "EHR Data is very important, and it would be great to have someone in our department working with it."
  
  > Her talk is clear and informative with details and visualization. The result section is a bit weak. The theoretical part and assumption need more explanations. Some simulations with noise need to be considered for the EHR data as well." 
  
  > "I had the opportunity to have lunch with Dr. Gronsbell, and it was apparent to me that she's an educator at heart.  She's clearly talented in research, given her training (PhD and postdoc) and current position, but she's also committed to being an educator and is returning to academia to fulfill this desire. The department would benefit from having a faculty member who has recent industry experience but has a passion for mentorship.  I thought her talk was clear, and I liked the way she handled questions from the audience first by repeating the question to make sure she understood it, then by providing a clear answer."
  
  > "She answers questions thoughtfully and thoroughly and makes sure she understands the question being asked first before rushing into an answer. Seems very meticulous."   

- Allison Meisner 

  > "She wasn't able to simplify when asked to re-explain and idea.  This is an important quality for teachers when teaching confused students."   
  
  > "Her presentation was clear even though I wasn't originally familiar with the research area. She seemed happy to answer questions from the audience and was clear with her answers.  She just seems like a really approachable person and someone students can feel comfortable going to with questions if they are lost in a class."   

- Zhengwu Zhang

  > "There were times in the presentation and while he was answering questions that I felt like the speaker's explanations were quite vague.  This could've been due to the complicated nature of the material and his desire not lose his audience among the weeds, but I'm not sure."
  
  > "He failed to give a clear explanation of the basic problem setting, even after prompting from the audience." 
  
  > "I liked his answer the question about his big picture goal.  His philosophy about research and finding what excites him and doing that daily resonates with me.  Students would benefit from an advisor with that mentality."     
  
  > "His talk was hard to follow. He took very little time to explain diffusion MRI. I feel like this talk was aimed at statisticians already very familiar with the scientific application and methods. Even then I would have a hard time following. I thought his research was interesting since I'm generally interested in the brain. But who knows, maybe in one on one research meetings he would clarify things."
  
- Sean Jewell 

- Lan Luo 
  
  > "I think her presentation was clear and she answered audience questions clearly, even though it was apparent that some didn't agree with her approach to the problem.  She seems approachable and like someone students could come to with questions if they were lost in a class."
  
  > "This talk was the most accessible for me, despite some substantial math."